### 2019-05-24 scache/tii/tex/model.tex
mkdir scache

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on. Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed computing frameworks mostly use DAGs to describe computation logic. 
A shuffle phase is required between each adjacent DAG computation phases. To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model can describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap shuffle phase one and map phases. We implemented this idea with SCache.
Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4). SCache starts pre-fetching and pre-scheduling in the map phase. This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase. According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

\begin{enumerate}
    \item 
    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
	The meaning of the inequality is that the speed of generating shuffle data (\(V_{Map} \times R\)) is greater than or equal to the shuffle speed (\(V_{Shuffle}\)). 
	In this situation, the shuffle phase is uninterrupted. The I/O resource will be fully utilized during the whole shuffle phase. As a result, the formula of \(T_{PShuffle}\) is as followed:
	\begin{equation}
		\label{equation_Tpshuffle1}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N}
		\end{aligned}
	\end{equation}

    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each round. In this case, the formula of \(T_{PShuffle}\) is as followed:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{enumerate}

@@

\subsection{Model Verification}\label{model_verification}
To verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}. (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node. To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop MapReduce framework. We deployed Hadoop with SCache and without SCache in both environments.

@@

>>>>

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc. The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_evaluation}, we will use the actual experimental results to evaluate the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
A shuffle phase is required between each adjacent DAG computation phases. To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model can describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

@@

Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap the shuffle phase and the map phases. We implemented this idea with SCache.
Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4). SCache starts pre-fetching and pre-scheduling in the map phase. This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase. According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

\begin{enumerate}
    \item \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1})

	The meaning of the inequality is that the speed of generating shuffle data (\(V_{Map} \times R\)) is greater than or equal to the shuffle speed (\(V_{Shuffle}\)). 
	In this situation, the shuffle phase is uninterrupted. The I/O resource will be fully utilized during the whole shuffle phase. As a result, the formula of \(T_{P\_Shuffle}\) is as followed:
	\begin{equation}
		\label{equation_Tpshuffle1}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N}
		\end{aligned}
	\end{equation}

    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2})

	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each round. In this case, the formula of \(T_{P\_Shuffle}\) is as followed:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{enumerate}

@@

\subsection{Model evaluation}\label{model_evaluation}
To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node. To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop MapReduce framework. We deployed Hadoop with SCache and without SCache in both environments.

@@

\begin{figure}
	\includegraphics[width=\linewidth]{fig/scache_util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
	\label{fig:scache_util}
\end{figure}

### 2019-05-24 scache/tii/tex/motivation.tex
mkdir scache

\textbf{Overview of shuffle process}. 
Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
The total number of buckets equals the number of reduce tasks in the successive step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.

%In short, shuffle is loosely coupled with application context and it's I/O intensive.
\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduce a significant latency to the application. 
Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

@@

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/util}
		\caption{Original Spark}
		\label{fig:util}
	\end{subfigure}
	\begin{subfigure}[b]{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/scache_util}
		\caption{Spark With SCache}
		\label{fig:scache_util}
	\end{subfigure}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
\end{figure*}

>>>>

% \textbf{Overview of shuffle process}

\subsubsection{Overview of shuffle process}
Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
The total number of buckets equals the number of reduce tasks in the successive step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.

%In short, shuffle is loosely coupled with application context and it's I/O intensive.
% \textbf{Impact of shuffle process}

\subsubsection{Impact of shuffle process}
Shuffle is I/O intensive, which might introduce a significant latency to the application. 
Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

@@

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
	\label{fig:util}
	\vspace{-1em}
\end{figure}

### 2019-05-24 scache/tpds/tex/abstract.tex
mkdir scache

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
The FRQ models utilization of resources and predicts the execution time of computing jobs on different DAG frameworks. 
We use the FRQ model to assist in analyzing DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

>>>>

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{black}
During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
The FRQ models utilization of resources and predicts the execution time of computing jobs on different DAG frameworks. 
We use the FRQ model to assist in analyzing DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{black}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

### 2019-05-24 scache/tpds/tex/intro.tex
mkdir scache

Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, 
the shuffle is often poorly optimized in practice.
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

>>>>

Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator}, 
the shuffle is often poorly optimized in practice.
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
